Benchmarks of the Non-Relativistic Hydrodynamics Algorithms in \thornado

### 2017-02-14 Documents/Euler/Benchmarks1D/draft.tex
Named test 2

\begin{abstract}
\thornado\ is a new astrophysical code for radiation-hydrodynamics based on high-order Runge-Kutta Discontinuous Galerkin (RKDG) methods.  
It currently solves the Euler equations for fluid dynamics and the two-moment ($M_{1}$) approximation of the radiative transfer equation. 
In this document, we benchmark the algorithms for solving the Euler equations.  
An extensive set of one-dimensional Riemann problems with known exact solutions were run, and the \thornado\ results were graphed and compared to exact solutions in cases where they exist. 
\end{abstract}

@@

Several tests were used to assess the accuracy of the integration method \citep{LiskaWendroff2003}. 
\begin{table}[h!]
\begin{center}
\begin{tabular}{ |c|c c c|c c c|c c| }
 \hline
 Test & $\rho_L$ & $u_L$ & $p_L$ & $\rho_R$ & $u_R$ & $p_R$ & $x_0$ & T \\
 \hline
 1 & 1 & 0 & 1 & 0.125 & 0 & 0.1 & 0.5 & 0.2 \\
 2 & 1 & 0.75 & 1 & 0.125 & 0 & 0.1 & 0.3 & 0.2 \\
 3 & 1 & -2 & 0.4 & 1 & 2 & 0.4 & 0.5 & 0.15 \\
 4 & 1 & 1 & $10^{-6}$ & 1 & -1 & $10^{-6}$ & 0.5 & 1 \\
 5 & 1 & -19.59745 & 1000 & 1 & -19.59745 & 0.01 & 0.8 & 0.012 \\
 6 & 5.99924 & 19.5975 & 460.894 & 5.99242 & -6.19633 & 46.095 & 0.4 & 0.035 \\
 7 & 1.4 & 0 & 1 & 1 & 0 & 1 & 0.5 & 2 \\
 8 & 1.4 & 0.1 & 1 & 1 & 0.1 & 1 & 0.5 & 2 \\
 9 & 0.1261192 & 8.9047029 & 782.92899 & 6.591493 & 2.2654207 & 3.1544874 & 0.5 & 0.0039 \\
10 & 5.6698 & 9.0299 & 100 & 1.0 & 0.0 & 1.0 & 0 & 1 \\
11 & 5.6698 & −1.4701 & 100 & 1.0 & -10.5 & 1.0 & 0 & 1 \\
 \hline
\end{tabular}
  \caption{table of tests \ee{Add more descriptive caption}}
  \label{tab:testtable}
\end{center}
\end{table}
$x_0$ refers to the position of the barrier. 
The computational domain $D$ is defined with $x_{\mbox{\tiny L}}=0.0$ and $x_{\mbox{\tiny R}}=1.0$ in tests 1--8, 0.1 to 0.6 in test 9 \citep{LiskaWendroff2003}, -5 to 15 in test 10, and -15 to 5 in test 11 \citep{Leveque2002}. 
\ee{Provide more detailed description of the Riemann problems and refer to Table~\ref{tab:testtable}}

@@

\subsection{Test 2}
For subsequent tests, the number of cells was consistent within each test, and the integration method was varied as in the first test. 
The graphs for the second test show a result common throughout many of the different tests: The first order integration method is considerably far from the exact solution; the second and third order integration methods yield nearly identical results which are near, but not exactly equal to, the exact solution. 
\begin{figure}[h]
  \begin{center}
     \includegraphics[width=.95\textwidth]{den_T2.png}	
  \end{center}
  \caption{Results showing the density for test 2 at $t=0.2$, computed with 100 cells with methods of different orders: 1st (solid red), 2nd (dashed green) and 3rd (dotted blue). The exact solution, obtained with Toro's Riemann solver, is given by the dash-dotted pink line.}
  \label{fig:den_T2}
\end{figure}

@@

\subsection{Test 13: Shock Entropy Waves}

>>>>

\begin{abstract}
The toolkit for high-order neutrino-radiation hydrodynamics (\thornado) is a code for astrophysical radiation-hydrodynamics based on high-order Runge-Kutta Discontinuous Galerkin (RKDG) methods.  
It currently solves the Euler equations for fluid dynamics and the two-moment ($M_{1}$) approximation of the radiative transfer equation. 
In this document, we benchmark the algorithms for solving the Euler equations.  
An extensive set of one-dimensional Riemann problems with known exact solutions were run, and the \thornado\ results were graphed and compared to exact solutions in cases where they exist. 
\end{abstract}

@@

Several tests were used to assess the accuracy of the integration method \citep{LiskaWendroff2003}. 
\begin{table}[h!]
\begin{center}
\begin{tabular}{ |c|c c c|c c c|c c| }
 \hline
 Test & $\rho_L$ & $u_L$ & $p_L$ & $\rho_R$ & $u_R$ & $p_R$ & $x_0$ & $T$ \\
 \hline
 1 & 1 & 0 & 1 & 0.125 & 0 & 0.1 & 0.5 & 0.2 \\
 2 & 1 & 0.75 & 1 & 0.125 & 0 & 0.1 & 0.3 & 0.2 \\
 3 & 1 & -2 & 0.4 & 1 & 2 & 0.4 & 0.5 & 0.15 \\
 4 & 1 & 1 & $10^{-6}$ & 1 & -1 & $10^{-6}$ & 0.5 & 1 \\
 5 & 1 & -19.59745 & 1000 & 1 & -19.59745 & 0.01 & 0.8 & 0.012 \\
 6 & 5.99924 & 19.5975 & 460.894 & 5.99242 & -6.19633 & 46.095 & 0.4 & 0.035 \\
 7 & 1.4 & 0 & 1 & 1 & 0 & 1 & 0.5 & 2 \\
 8 & 1.4 & 0.1 & 1 & 1 & 0.1 & 1 & 0.5 & 2 \\
 9 & 0.1261192 & 8.9047029 & 782.92899 & 6.591493 & 2.2654207 & 3.1544874 & 0.5 & 0.0039 \\
10 & 5.6698 & 9.0299 & 100 & 1.0 & 0.0 & 1.0 & 0 & 1 \\
11 & 5.6698 & −1.4701 & 100 & 1.0 & -10.5 & 1.0 & 0 & 1 \\
 \hline
\end{tabular}
  \caption{table of tests \ee{Add more descriptive caption}}
  \label{tab:testtable}
\end{center}
\end{table}
$x_0$ refers to the position of the barrier. 
The computational domain $D$ is defined with $x_{\mbox{\tiny L}}=0.0$ and $x_{\mbox{\tiny R}}=1.0$ in tests 1--8, 0.1 to 0.6 in test 9 \citep{LiskaWendroff2003}, -5 to 15 in test 10, and -15 to 5 in test 11 \citep{Leveque2002}. 
\ee{Provide more detailed description of the Riemann problems and refer to Table~\ref{tab:testtable}}

@@

\subsection{Test 2: Toro's Riemann Problem}

This test is the same as Sod's shock tube from the previous section, except that there is a non-zero velocity to the left of the initial discontinuity.  
As a result, a sonic point develops in the rarefaction wave.  
For subsequent tests, the number of cells was consistent within each test, and the integration method was varied as in the first test. 
The graphs for the second test show a result common throughout many of the different tests: The first order integration method is considerably far from the exact solution; the second and third order integration methods yield nearly identical results which are near, but not exactly equal to, the exact solution. 
\begin{figure}[h]
  \begin{center}
     \includegraphics[width=.95\textwidth]{den_T2.png}	
  \end{center}
  \caption{Results showing the density for test 2 at $t=0.2$, computed with 100 cells with methods of different orders: 1st (solid red), 2nd (dashed green) and 3rd (dotted blue). The exact solution, obtained with Toro's Riemann solver, is given by the dash-dotted pink line.}
  \label{fig:den_T2}
\end{figure}

@@

\subsection{Test 13: Shock-Entropy Wave Interaction}
